Product plots

### 2011-03-30 prodplots-infovis.tex
Fix name of package\!

We have provided a reference implementation of these ideas in an R \citep{R} package called {\tt prodplots}, available from {\tt http://github.com/hadley/prodplots}. There are two main functions: {\tt prodcalc}, which computes the coordinates of each rectangle; and {\tt prodplot}, which displays the rectangles with the ggplot2 package \citep{me:ggplot2}. The code is well tested, and ensures that the constraints are always satisfied. The {\tt prodplots} code to used to create the images in this paper is available from the authors.

The {\tt prodplots} package has been designed to be flexible and extensive.  For example, each graphical primitive is represented by a function: {\tt hspine()}, {\tt vspine()}, {\tt spine()}, {\tt hbar()}, {\tt vbar()}, {\tt tile()} and {\tt fluct()}. Adding a new graphical primitive is easy: you just write a new function, and can use the existing calculation and display algorithms.

>>>>

We have provided a reference implementation of these ideas in an R \citep{R} package called {\tt productplots}, available from {\tt http://github.com/hadley/productplots}. There are two main functions: {\tt prodcalc}, which computes the coordinates of each rectangle; and {\tt prodplot}, which displays the rectangles with the ggplot2 package \citep{me:ggplot2}. The code is well tested, and ensures that the constraints are always satisfied. The {\tt productplots} code to used to create the images in this paper is available from the authors.

The {\tt productplots} package has been designed to be flexible and extensive.  For example, each graphical primitive is represented by a function: {\tt hspine()}, {\tt vspine()}, {\tt spine()}, {\tt hbar()}, {\tt vbar()}, {\tt tile()} and {\tt fluct()}. Adding a new graphical primitive is easy: you just write a new function, and can use the existing calculation and display algorithms.
